\documentclass[12pt,letterpaper]{article}
\author{Shawn Ma}
\date{\today}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[letterspace=150]{microtype}
%\usepackage{asymptote}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{wasysym}

\geometry{left=2cm,right=2cm,top=1.5cm,bottom=1.5cm}
\begin{document}
%不要自动缩进
\setlength{\parindent}{0pt}
\setstretch{1.25}

\begin{large}
\begin{enumerate}
    \item For each equation below, fill in the blank numerator or denominator
    so that the equation is true.
    \begin{multicols}{2}
    \begin{enumerate}
        \item $\cfrac{7}{9}=\cfrac{\hspace{1cm}}{27}$
        \item $\cfrac{12}{42}=\cfrac{2}{\hspace{1cm}}$
        \item $\cfrac{56}{40}=\cfrac{\hspace{1cm}}{10}$
        \item $\cfrac{6}{5}=\cfrac{72}{\hspace{1cm}}$
        \item $\cfrac{28}{42}=\cfrac{2}{\hspace{1cm}}=\cfrac{\hspace{1cm}}{9}=\cfrac{18}{\hspace{1cm}}$
        \item $\cfrac{24}{30}=\cfrac{\hspace{1cm}}{20}$
    \end{enumerate}
\end{multicols}

    \item Compared each pair of fractions below.
    \begin{multicols}{2}
        \begin{enumerate}
            \item $\cfrac{3}{5}{\huge\Circle}\cfrac{4}{5}$
            \item $\cfrac{3}{8}{\huge\Circle}\cfrac{3}{9}$
            \item $\cfrac{3}{4}{\huge\Circle}\cfrac{5}{8}$
            \item $\cfrac{3}{5}{\huge\Circle}\cfrac{11}{15}$
            \item $\cfrac{12}{27}{\huge\Circle}\cfrac{4}{9}$
            \item $\cfrac{15}{23}{\huge\Circle}\cfrac{5}{8}$
            \item $\cfrac{40}{55}{\huge\Circle}\cfrac{7}{11}$
            \item $\cfrac{2}{3}{\huge\Circle}\cfrac{32}{45}$
            \item $\cfrac{45}{81}{\huge\Circle}\cfrac{5}{7}$
            \item $\cfrac{25}{39}{\huge\Circle}\cfrac{8}{13}$
        \end{enumerate}
    \end{multicols}

    \item Add and simplify.
    \begin{multicols}{2}
        \begin{enumerate}
            \item $\cfrac{4}{6}+\cfrac{1}{6}=$
            \item $\cfrac{1}{11}+\cfrac{1}{11}=$
            \item $\cfrac{2}{5}+\cfrac{1}{5}=$
            \item $\cfrac{4}{15}+\cfrac{8}{15}=$
            \item $\cfrac{2}{7}+\cfrac{3}{7}=$
            \item $\cfrac{7}{12}+\cfrac{1}{12}=$
            \item $\cfrac{3}{8}+\cfrac{5}{8}=$
            \item $\cfrac{2}{9}+\cfrac{4}{9}=$
        \end{enumerate}
    \end{multicols}

    \pagebreak
    \item On the morning of April 5th, $\frac{1}{10}$
     inches of rain fell on Beast Island. Later that day,
     another $\frac{7}{10}$ inches of rain fell.
      How many rain fell on Beast Island on April 5th?
      \\
    \\

      \item Ally mixes $\frac{3}{8}$ cups of granola with 
      $\frac{1}{8}$ cups of chocolate bits and $\frac{3}{8}$
       cups of mixed nuts to make trail mix for her hiking 
       trip. How many cups of trail mix does she make?
\\
\item A 15-ounce bag of potato chips contains 6 servings. How many ounces of chips are in each serving?\\\\
\item What is the side length in inches of a square with a perimeter of 39 inches?\\\\
\item Grogg cuts a 22-inch rope into three pieces of equal length. How many inches long is each piece?\\\\
\item Four identical bags of Beastie Puffs cereal weigh a total of 21 ounces. How many ounces does each bag of cereal weigh?\\\\
\item Brenda makes some candles using 28 ounces of wax. She uses half the wax to make 2 large candles, and she uses the rest to make 4 identical small candles. How many ounces of wax are there in each small candle?

\pagebreak

\item Count by 11ths starting from $\cfrac{1}{11}$.
\newcommand\answerbox{%%
    \fbox{\rule{0.7cm}{0pt}\rule[-2ex]{0pt}{6ex}}}
\[
\cfrac{1}{11},\cfrac{2}{11},\cfrac{3}{11},\answerbox,\answerbox,\answerbox,\answerbox
\]
\end{enumerate}
\end{large}
\end{document}