\documentclass[letterpaper,12pt]{article}
\author{Shawn Ma}
\date{\today}

\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{asymptote}
\usepackage{geometry}
\usepackage{enumitem}

\geometry{left=2cm,right=2cm,top=1.5cm,bottom=1.5cm}
\begin{document}
%不要自动缩进
\setlength{\parindent}{0pt}
\begin{enumerate}
    \item Find all values of $t$ such that $t-1$, $t+1$ and $4$ 
    could be the lengths of the sides of a right triangle.
    \item Find all $a$ such that
    \[\frac{3}{1-\sqrt{a-2}}+\frac{3}{1+\sqrt{a-2}}=6\]
    \item Find $(x,y)$ such that \begin{align*}
        x+y &=6 \\
        x^2+xy+2y^2&=32
         \end{align*}
    \item Solve the system of equations: \begin{align*}
    x+2y-z&=5\\
    3x+2y+z&=11\\
    (x+2y)^2-z^2&=15
    \end{align*}
    \item Solve the system of equations: \begin{align*}
        r^2-2rs&=27\\
        rs-2s^2&=9
        \end{align*}
    \item Find the value of $a^3b^7c^{14}$ given that $a^3b^2c=108$ and $a^2b^3c^5=240$.
    \item Let $f(x)=\cfrac{x+1}{x-1}$. Assume $|x|\neq{1}$, simplify $f(x)\cdot f(-x)$.
    \item A function $g(x)$ is defined for $-3\le x\le 4$ such that $g(x)=(2+x)^2$. Find the range of $g$.
    \item If function $y=x^2-3x-4$ has the domain of $[0,m]$ and its range is $[-\cfrac{25}{4},-4]$, what is the possible
    value range of $m$?
    \item Find the domain and range of the following real valued functions:
    \begin{enumerate}
       \item $f(x)=|1-x|$
       \item $f(t)=\sqrt{2-t}$
       \item $h(x)=1-x^2$
    \end{enumerate}
    \item If $f(a)=a-2$ and $F(a,b)=b^2+a$, find the value of $F(3,f(4))$.
    \item Let $f(x)$ be a real valued function. $f(0)=1$. For any value $x,y\in R$ we have \[
    f(x-y)=f(x)-y(2x-y+1)\] Find the expression of $f(x)$.
    \item Let $f(x-\cfrac{1}{x})=x^2+\cfrac{1}{x^2}$. Find $f(3)$.
    \item Let $f(\cfrac{x}{3})=\cfrac{2x+3}{x}$, find $f^{-1}(\cfrac{x}{3})$.
    \item Let $f(x)=x^2-2x$ and $g(x)=\sqrt{1-x}$.
        \begin{enumerate}
            \item Find $f(g(x))$
            \item Is $g(f(-2))$ undefined? why and why not.
            \item Find the domain of $f(g(x))$
        \end{enumerate}
    \item Suppose $h, f$ and $g$ are functions such that $h(x)=f(g(x))$. If $(3,0)$ is the only x-intercept of the graph of $g$,
    can we determine the x-intercepts of y-intercepts of $h$?
    \item Does the function $g(x)=2x^2-9$ has an inverse? if yes, find it, otherwise explain why.
    \item Does the function $h(x)=3\sqrt{2x+1}$ has an inverse? if yes, find it, otherwise explain why.
    \item Let $f(x)=\cfrac{-5-x}{3-2x}$. Find $f^{-1}(7)$ without finding $f^{-1}(x)$.
\end{enumerate}


\end{document}